A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-12 paper.tex
small change:

\textbf{Dimension 3}
\begin{itemize}
 \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} There is a minimal twist in dimension 3 which can be defined with $\mc N=2$ supersymmetry, including a chiral multiplet valued in a representation $R$.  This twist is perturbatively equivalent to a generalized form of BF theory with one real direction and one complex holomorphic direction, coupled to a generalized $\beta \gamma$-system valued in $R$.  This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.  If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.  Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
 \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.  The first is a perturbatively trivial theory which we refer to as the A-twist, obtained by dimensional reduction from the 4d A-twist.  This theory fits into a non-trivial family deforming the minimal twist, which is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.  This twist was studied by Blau and Thompson \cite{BlauThompson1}, where it is referred to as a Casson invariant model, as well as Kapustin and Vyas \cite{KapustinVyas} as a dimensional reduction of Donaldson-Witten theory.
 \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The remaining topological twist is perturbatively equivalent to the 3d topological BF theory coupled to a symplectic boson valued in symplectic representation $U$.  It is $\spin(3;\RR)$-invariant, and can be defined on arbitrary 3-manifolds. This form of twist was studied by Rozansky and Witten, \cite{RozanskyWitten} as well as by Blau and Thompson \cite{BlauThompson2}.
\end{itemize}

\textbf{Dimension 2}
\begin{itemize}
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.} There is a holomorphic twist in dimension 2 which can be defined with $\mc N=(2,2)$ supersymmetry, including a chiral multiplet valued in a representation $R$.  This twist is perturbatively equivalent to a holomorphic BF theory coupled to a $\beta \gamma$-system valued in $R$.  More specifically: to holomorphic BG theory valued in the tangent space $T[1]R/\gg$.  This theory is $\mr U(1)$-equivariant, and can be defined on any Riemann surface.  If the supersymmetry is promoted to $\mc N=(4,4)$, with $R = U \oplus \gg$ for a symplectic representation $U$, then the twisted theory can now be modelled by holomorphic BF theory coupled to a holomorphic symplectic boson.  Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with holomorphic BF theory valued in $T[1]T^*[2](\gg/\gg))$.  The study of twists of 2d $\mc N=(2,2)$ supersymmetric field theories goes back to work of Eguchi and Yang \cite{EguchiYang} and Witten \cite{Wittenmirror}.
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological A twist.} In each of these cases, the minimal twist can again be deformed to a topological theory in two inequivalent ways.  The first is a perturbatively trivial theory: the A-model valued in the cotangent space to the quotient stack $R/\gg$.
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) topological B twist.} The remaining topological twist, the B-twist, is perturbatively equivalent to a 2d topological BF theory, coupled a topological matter valued in the representation $R$.
 \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} Chiral theories in 2-dimensions only admit a holomorphic twist.  These twists can all be realised as holomorphic BF theory on $\CC$, coupled to a holomorphic $\beta \gamma$-system (in the case where the chiral theory includes matter), or to a holomorphic free fermion (in the case where the chiral theory is pure gauge with $\mc N=(0,N_-)$ supersymmetry). Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{Wittenmirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
\end{itemize}

@@

\item The BRST action is $S_{\mr{BRST}} = 0$.
\end{itemize}
We denote the space of BV fields by $\cE = \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, T^*[d] B\fg)$, where $d = \dim_\CC(X) + 2\dim_\CC(Y) + \dim(M) - 1$.
\label{def:generalizedBF}
\end{definition}

@@

We will now concentrate on the 7-dimensional case.

@@

\textsc{University of Massachusetts, Amherst}\\
\textsc{Department of Mathematics and Statistics, 710 N Pleasant St, Amherst, MA 01003}\\
\texttt{celliott@math.umass.edu}\\
\vspace{-5pt}

\textsc{Institut f\"ur Mathematik, Universit\"at Z\"urich}\\
\textsc{Winterthurerstrasse 190, 8057 Z\"urich, Switzerland}\\
\texttt{pavel.safronov@math.uzh.ch}\\
\vspace{-5pt}

\textsc{Northeastern University}\\
\textsc{Department of Mathematics, 360 Huntington Ave, Boston, MA 02115}\\
\texttt{brianwilliams.math@gmail.com}\\

>>>>

\textbf{Dimension 3}
\begin{itemize}
 \item \emph{$\mc N=2$, $\mc N=4$ and $\mc N=8$ minimal twist.} There is a minimal twist in dimension 3 which can be defined with $\mc N=2$ supersymmetry, including a chiral multiplet valued in a representation $R$.  This twist is perturbatively equivalent to a generalized form of BF theory with one real direction and one complex holomorphic direction, coupled to a generalized $\beta \gamma$-system valued in $R$.  This theory is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.  If the supersymmetry is promoted to $\mc N=4$, with $R = U \oplus \gg$ for a symplectic representation $U$, and the twisted theory is modelled by a generalized BF theory now coupled to a generalized symplectic boson.  Finally, if $U = T^*\gg$ the supersymmetry lifts to $\mc N=8$, and the twisted theory can be identified with generalized BF theory valued in $T[1](\gg/\gg)$.
 \item \emph{$\mc N=4$ and $\mc N=8$ topological A twist.} If $\mc N$ is at least 4, this minimal twist can be deformed in two inequivalent ways.  The first is a perturbatively trivial theory which we refer to as the A-twist, obtained by dimensional reduction from the 4d A-twist.  This theory fits into a non-trivial family deforming the minimal twist, which is $\mr U(1)$-equivariant, and can be defined on the product of a Riemann surface and a flat 1-manifold.  This twist was studied by Blau and Thompson \cite{BlauThompson1}, where it is referred to as a Casson invariant model, as well as Kapustin and Vyas \cite{KapustinVyas} as a dimensional reduction of Donaldson-Witten theory.
 \item \emph{$\mc N=4$ and $\mc N=8$ topological B twist.} The remaining topological twist is perturbatively equivalent to the 3d topological BF theory coupled to a symplectic boson valued in symplectic representation $U$.  It is $\spin(3;\RR)$-invariant, and can be defined on arbitrary 3-manifolds. This form of twist was studied by Rozansky and Witten, \cite{RozanskyWitten} as well as by Blau and Thompson \cite{BlauThompson2}.
\end{itemize}

\textbf{Dimension 2}
\begin{itemize}
 \item \emph{Non-Chiral ($\mc N=(2,2), (4,4), (8,8)$) holomorphic twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological A twist.}
 \item \emph{Non-Chiral ($\mc N=(4,4), (8,8)$) topological B twist.}
 \item \emph{Chiral $\mc N=(0,N_-)$ holomorphic twist.} 
Twisted $(0,2)$ $\sigma$-models were first studied by Witten in \cite{WittenMirror}, and can be used to obtain the chiral algebra of chiral differential operators \cite{WittenCDO}. 
\end{itemize}

@@

\item The BRST action is $S_{\mr{BRST}} = 0$.
\end{itemize}
We denote the space of BV fields by $T^*[-1] \map(X\times Y_{\mr{Dol}}\times M_{\mr{dR}}, B\fg)$.
\label{def:generalizedBF}
\end{definition}

@@

The 7-dimensional result immediately follows.

@@
